### 2021-06-28 src/paper/appendix_data.tex
Add bullet points for synthetic population.

>>>>

\begin{itemize}
    \item \textcolor{red}{Describe microcensus campus file and which data we use and for what}
    \item \textcolor{red}{Describe size and sampling of households}
    \item \textcolor{red}{counties are randomly drawn}\comment[id=K]{Find out why!}
    \item \textcolor{red}{how we create the occupation column}
    \item \textcolor{red}{describe how we create the contact model group ids for school,
    work and other}
    \item \textcolor{red}{Describe work contact priority, educ contact priority and
    rapid test compliance parameter and quarantine compliance.}
    \item \textcolor{red}{vaccination rank creation}
\end{itemize}
